Software Citation Principles

### 2016-03-08 sc-principles/software-citation-principles.tex
small style stuff and abbreviation expansion in 3 and 4

@@

domain groups include bioCADDIE~\cite{bioCADDIE}, Computational Infrastructure for Geodynamics~\cite{CIG}, etc.;
``repository'' refers to public software repositories such as ASCL~\cite{ascl},
GitHub, Netlib, CRAN, institutional repositories;

@@

In a blog post from 2012, \cite{ssi-how-to-cite} discusses some of the pitfalls of trying to cite software in publications.
The author includes useful guidance for when to consider citing software as well as some ways to help `convince' journal editors
to allow the inclusion of software citations.

In \cite{ssi-citation-files}, Wilson suggests that software authors include a `CITATION' file that documents exactly how the
authors of the software would like to be cited by others. While this isn't a formal metadata specification (it's not machine
readable for example) this does offer a solution for authors wishing to give explicit instructions to potential citing authors.\dmnote{There is evidence from databases that people actually tend to follow such instructions if they exist: \cite{10.1371/journal.pone.0136631}.} \katznote{adding this ref to the introduction - not sure if it is still needed here too}
In a later post on the SSI blog, Jackson \cite{ssi-how-shalt-i-cite-thee} gives a good overview of some of the approaches
package authors have taken to automate the generation of citation entities such as bibtex entries.
\scnote{So does \cite{knepley2013accurately}}

@@

\asnote{Should also discuss the WSSSPE \cite{wssspe} series of workshops in this section}
\scnote{Section 5.8 and Appendix J in \cite{WSSSPE3} has some preliminary work and discussion on the topic.}

@@

AAS workshop \cite{aas-software-index}, CRediT project \cite{casrai-credit}, Ontosoft \cite{ontosoft}
\acmnote{ CodeMeta? }

>>>>

\hyphenation{bioCADDIE}

@@

domain groups include bioCADDIE~\cite{bioCADDIE}, Computational Infrastructure for Geodynamics (CIG)~\cite{CIG}, etc.;
``repository'' refers to public software repositories such as Astronomy Source Code Library (ASCL)~\cite{ascl},
GitHub, Netlib, Comprehensive R Archive Network (CRAN), institutional repositories;

@@

In a blog post from 2012, Jackson discusses some of the pitfalls of trying to cite software in publications~\cite{ssi-how-to-cite}.
He includes useful guidance for when to consider citing software as well as some ways to help `convince' journal editors
to allow the inclusion of software citations.

Wilson suggests that software authors include a `CITATION' file that documents exactly how the
authors of the software would like to be cited by others~\cite{ssi-citation-files}. While this isn't a formal metadata specification (it's not machine
readable for example) this does offer a solution for authors wishing to give explicit instructions to potential citing authors.\dmnote{There is evidence from databases that people actually tend to follow such instructions if they exist: \cite{10.1371/journal.pone.0136631}.} \katznote{added this ref to the introduction - not sure if it is still needed here too}
In a later post on the SSI blog, Jackson gives a good overview of some of the approaches
package authors have taken to automate the generation of citation entities such as bibtex entries~\cite{ssi-how-shalt-i-cite-thee},
and Knepley at al. do similarly~\cite{knepley2013accurately}.

@@

\asnote{Should also discuss the WSSSPE~\cite{wssspe} series of workshops in this section}
\scnote{Section 5.8 and Appendix J in \cite{WSSSPE3} has some preliminary work and discussion on the topic.}

@@

AAS workshop~\cite{aas-software-index}, Project CRediT~\cite{casrai-credit}, Ontosoft~\cite{ontosoft}
\acmnote{ CodeMeta? }
